Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Minor edit in number of tesseroids caption

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/number-of-tesseroids.pdf}
\caption{
    Number of discretizations performed by the density-based algorithm in case of
    (a)~exponential densities with the same values of $b$ shown in
    Fig.~\ref{fig:exp-densities},
    (b)~sinusoidal densities with the same values of $b$ shown in
    Fig.~\ref{fig:sine-densities}.
    On both figures the boundaries of the discretized tesseroids are marked with orange
    dots.
    Subfigure (c) shows the number of discretized tesseroids for the sinusoidal
    densities as a function of the factor $b$.
}
\label{fig:number-of-tesseroids}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/number-of-tesseroids.pdf}
\caption{
    Number of discretizations performed by the density-based algorithm
    (with a $\delta = 0.1$) in case of
    (a)~exponential densities with the same values of $b$ shown in
    Fig.~\ref{fig:exp-densities},
    (b)~sinusoidal densities with the same values of $b$ shown in
    Fig.~\ref{fig:sine-densities}.
    On both figures the boundaries of the discretized tesseroids are marked with orange
    dots.
    Subfigure (c) shows the number of discretized tesseroids for the sinusoidal
    densities as a function of the factor $b$.
}
\label{fig:number-of-tesseroids}
\end{figure*}
